Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/type-theory.tex
[ paper ] type theory section.

\begin{notation}
We use \Prop for the type of propositions and the dependent type, $Γ ⊢ φ$ for
theorems where $Γ : \List~\Prop$ and $φ : \Prop$.
$\abbre{List}$ type is the usual inductive type for lists.
For syntactical equivalence, we write the equality as $φ ≡ ψ$
for $φ,~ψ : \Prop$. For this equality, we assume the
reflexivity, symmetry and transitivity properties.
\end{notation}

@@

\begin{notation}
The type of natural numbers is called \Nat, and it is defined as
usual, where $\zero$ and $\suc$ are its data constructors. We use names
and symbols for the arithmetic operations as usual ($+$, $-$, $*$).
We include syntax sugar for $\zero$, $\suc$, $\suc~\zero$,
$\cdots$, with the decimal representation: $0$, $1$, $2$, $\cdots$
as well.
\end{notation}

@@

>>>>

@@

\begin{notation}

We use \Prop for the type of propositions.
For syntactical equivalence, we write the equality as $φ ≡ ψ$
for $φ,~ψ : \Prop$. For this equality, we assume the
reflexivity, symmetry and transitivity properties.

\end{notation}

\begin{notation}

The type of natural numbers is called \Nat, and it is defined as
usual, where $\zero$ and $\suc$ are its data constructors. We use names
and symbols for the arithmetic operations as usual ($+$, $-$, $*$).
We include syntax sugar for $\zero$, $\suc$, $\suc~\zero$,
$\cdots$, with the decimal representation: $0$, $1$, $2$, $\cdots$
as well.

\end{notation}

@@

\begin{notation}
We write theorems as the family of dependent types, $Γ ⊢ φ$ where
the turnstile symbol (⊢) represents the syntactical consequence relation
between a set of premises, $Γ : \List~\Prop$ and a conclusion $φ : \Prop$.
$\abbre{List}$ type is the usual inductive type for lists.
\end{notation}
